Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-06-06 paper-v1.tex
playing with BibTeX

An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8]. As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1]. Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]:
\paragraph{Decentralisation}Taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process;
\paragraph{Immutability} of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper;
\paragraph{Transparency} (meaning that we have a viewable record of all the transactions), would also make editorial decisions (publish or not publish a study) more transparent and democratic. Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers. From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).

@@

\newline Externally Owned Accounts (EOA) in Ethereum are controlled by private keys, are 20 bytes long and have no code. An user can send messages from an externally owned account by creating and signing a transaction.
\newline The limitation of such solution regarding the Privacy of the Protocol is due to the fact that blockchain and transactions are public so anyone can see the details of a transaction, browsing a block explorer like Etherscan, and also they're subjected to data mining to extract value and identify users in the blockchain.
\newline To avoid that, AntsReview will implement zkAnt, an Ant token wrapped into AZTEC Protocol, where leveraging on zkSNARKS, and PLONK in the future, will allow private transactions in the system to maintain the privacy and anonimiy of Peer-Reviewers.
\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses ZK-SNARKS to validate encrypted transactions.
\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
\newline Zero-Knowledge proofs allow an actor (prover) to prove to another (verifier) that a statement is true, without revealing any information apart from the validity of the statement itself.
\newline Future developements will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability. This will enable to run smart contracts at scale with quasi-instant transactions while still being secured by Ethereum.

>>>>

An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8]. As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1]. Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]:
\paragraph{Decentralisation}Taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process;
\paragraph{Immutability} of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper;
\paragraph{Transparency} (meaning that we have a viewable record of all the papers and peer-reviews), would also make editorial decisions (publish or not publish a study) more transparent and democratic. Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers. From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).

@@

 Externally Owned Accounts (EOA) in Ethereum are controlled by private keys, are 20 bytes long and have no code. An user can send messages from an externally owned account by creating and signing a transaction.
\newline The limitation of such solution regarding the Privacy of the Protocol is due to the fact that blockchain and transactions are public so anyone can see the details of a transaction, browsing a block explorer like Etherscan, and also they're subjected to data mining to extract value and identify users in the blockchain.
\newline To avoid that, AntsReview will implement zkAnt, an Ant token wrapped into AZTEC Protocol, where leveraging on zkSNARKS, and PLONK in the future, will allow private transactions in the system to maintain the privacy and anonimiy of Peer-Reviewers.
\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses ZK-SNARKS to validate encrypted transactions.
\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
\newline Zero-Knowledge proofs allow an actor (prover) to prove to another (verifier) that a statement is true, without revealing any information apart from the validity of the statement itself.
\newline Future developements will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability. This will enable to run smart contracts at scale with quasi-instant transactions while still being secured by Ethereum.
